Incentives are the biggest barriers to widespread data sharing.

### 2021-04-09 new-paper.Rmd
add author contributions and competing interests

>>>>

# Author Contributions

Both authors contributed equally to the work, making substantial contributions to the conception, design, drafting and revision of the work. The authors have approved the submitted version, and have agreed both to be personally accountable for the author's own contributions and to ensure that questions related to the accuracy or integrity of any part of the work, even ones in which the author was not personally involved, are appropriately investigated, resolved, and the resolution documented in the literature.

# Competing Interests

The authors declare no competing interests.
